An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/intro.tex
config: intro

Our \app prototype still has a few limitations:
for example, we cannot handle configuration errors that can be 
triggered during system execution time.
Nevertheless, we believe \app may suggest a practical path
toward automatic and modular language-based configuration verification.
To summarize, this tool paper makes the following contributions:

@@

\item \app is capable of detecting various tricky errors that cannot
be detected by previous efforts,
including ordering errors, fine-grained value correlation errors, 
entry missing errors, and environment-related errors.

\item We implement a \app prototype and evaluate it by
conducting comprehensive experiments.

>>>>

Our \app prototype still has many limitations:
for example, we cannot handle configuration errors that can be 
triggered during system execution time.
Nevertheless, we believe \app may suggest a practical path
toward automatic and modular language-based configuration verification.
To summarize, this tool paper makes the following contributions:

@@

\item \app is capable of detecting various tricky errors that cannot
be detected by previous efforts,
including entry ordering errors, fine-grained value correlation errors, 
entry missing errors, and environment-related errors.

\item We implement a \app prototype and evaluate it by
conducting comprehensive experiments on real-world dataset.
